Suppl. Figure 3. & 4. Mirobiome-KEGG correlations.

### 2022-10-04 reports/manuscript/Suppl.Figure4-5.Rmd

```{r message=FALSE, warning=FALSE}
##################
# LOAD LIBRARIES #
##################
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  library(tidyverse)
  library(openxlsx)
  library(fgsea)
  library(rafalib)
  library(Rcpp)
  #remotes::install_github("czarnewski/niceRplots",force=T)
  library(niceRplots)
})  })  })

>>>>

```{r message=FALSE, warning=FALSE}
##################
# LOAD LIBRARIES #
##################
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  library(tidyverse)
  library(openxlsx)
  library(fgsea)
  library(rafalib)
  library(Rcpp)
  library(igraph)
  #remotes::install_github("czarnewski/niceRplots",force=T)
  library(niceRplots)
  library(parallel)
})  })  })
